Personalization and probabilities: impersonal propensities in online grocery shopping

### 2018-05-22 log.rmd
fixing references for proofs
fixing proofs

>>>>

## Wed 16 May 2018 19:09:07 BST
- doing proofs  BDS778310.pdf 
- TODO:  
    - look up Sarwar conference location
    - Ardissono editors, etc.Goy, Anna, Liliana Ardissono, and Giovanna Petrone. ‘Personalization in E-Commerce Applications’. In The Adaptive Web, edited by P. Brusilovsky, A. Kobsa, and W Nejdl, 485–520. Springer, 2007.

## Tue 22 May 2018 14:29:45 BST
- doing proofs again -- there were some more typos, etc.
